### 2015-05-14 paper.tex
finished proof, will clean up in a bit

We know all points in $T$ are within $\frac{\beta\text{OPT}}{2|C^*_i|}$ of $c_i^*$ because at least some are in the inner ring of $C^*_i$. Following from \ref{lemma:4.2a} and \ref{emma:4.2b}, it is then impossible for a point to exist that is further than $\frac{\beta\text{OPT}}{2|C^*_i|}$ from $c_i^*$. This immediately implies that $T \subset C_i^*$ because $C_i^*$ is beta distributed. Additionally we have that all points in B(T) are less than $2r$ away from some point in $T$. Because we established $2r = \frac{\beta\text{OPT}}{4s} \leq \frac{\beta\text{OPT}}{2|C_i^*|}$, all points in B(T) then within $ \frac{\beta\text{OPT}}{|C_i^*|}$ of $c_i^*$, and therefor within $C_i^*$.

@@

>>>>

We know all points in $T$ are within $\frac{\beta\text{OPT}}{2|C^*_i|}$ of $c_i^*$ because at least some are in the inner ring of $C^*_i$. Following from \ref{lemma:4.2a} and \ref{lemma:4.2b}, it is then impossible for a point to exist that is further than $\frac{\beta\text{OPT}}{2|C^*_i|}$ from $c_i^*$. This immediately implies that $T \subset C_i^*$ because $C_i^*$ is beta distributed. Additionally we have that all points in B(T) are less than $2r$ away from some point in $T$. Because we established $2r = \frac{\beta\text{OPT}}{4s} \leq \frac{\beta\text{OPT}}{2|C_i^*|}$, all points in B(T) then within $ \frac{\beta\text{OPT}}{|C_i^*|}$ of $c_i^*$, and therefor within $C_i^*$.

@@

\subsubsection{The algorithm outputs a k-clustering with cost $\leq (1+\epsilon)OPT$}

In order to show this we will compare the total cost of clusters $\mathcal{C}$ Derived by $T_1, ..., T_k$ with those of $\mathcal{C}^*$. We know that the expensive clusters $C_i$ have centers $c_i^*$, and so its total cost will not exceed $\text{OPT}_i$.

The cost of a cheap cluster is $\sum\limits_{x\in T\cup B(T)}d(x, c_i) + \sum\limits_{x \in C_i^* and x\notin T\cup B(T)}d(x, c_i)$. Because all points in the first term are in the innter ring, that includes the center, so $\sum\limits_{x\in T\cup B(T)}d(x, c_i) \leq \sum\limits_{x\in T\cup B(T)}d(x, c^*_i)$. We must show the error in $\sum\limits_{x \in C_i^* and x\notin T\cup B(T)}d(x, c_i)$ is bounded by $(1+\epsilon)$.

We will show that $d(c_i, c_i*) < \epsilon\frac{\beta\text{OPT}}{8|C_i^*|}$ for a cheap cluster. We know by the definition of a cheap cluster that the cost is at most $(\epsilon/32)\beta\text{OPT}/|C_i^*|$. In order not exceed this bound, at least half of the points have distance at most $(\epsilon/16)\beta\text{OPT}/|C_i^*|$ from $c_i^*$. Also these are by definition in the inner ring. We know that at least half the points in a cheap cluster reside in the inner ring. If $d(c_i, c_i^*)  \geq \epsilon\frac{\beta\text{OPT}}{8|C_i^*|}$, then we require at least half of the points to contribute at least $(\epsilon/16)\beta\text{OPT}/|C_i^*|$ to the sum, which means some point in the inner ring must do so. Therefor $\sum\limits_{x\in T\cup B(T)}d(x, c_i)> OPT_i$, which contradicts the optimality of the inner ring points.

We therefor for each $x \in C_i^* and x\notin T\cup B(T)$ we have $d(c_i, c_i^*) \leq \epsilon\frac{\beta\text{OPT}}{8|C_i^*|}$. So $d(x, c_i) \leq d(x, c_i^*) + d(c_i^*, c_i) \leq (1+\epsilon)d(x,c_i^*)$. And so each point adds at most a factor of $(1+\epsilon)$ to the error, bounding our total error to $(1+\epsilon)\text{OPT}$
